\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Fix wording
Fix singular/plural

      \item[-] \textbf{Added:} Date and time when the membership was first established .
      \item[-] \textbf{Entry:} If membership was established through screening (see section \ref{sec:membership_curation}), the this is set to ID of screening authority which created membership. If it was established through screening (see section \ref{sec:paid_membership}), then this is the paid term ID of the terms. Otherwise its blank.
      \item[-] \textbf{BRAQs Instances:} Set of BRAQ instances for all base member actions (see section \ref{sec:BRAQ})
      \item[-] \textbf{Suspended:} Whether member is suspended.
      \item[-] \textbf{Subscription:} If at least one subscription has been entered into, then this is the date and time of this, and the corresponding subscription term ID (see section \ref{sec:subscription}). Otherwise its blank.
    \end{itemize}
\end{concept_box}

@@

The governance process is divided into a sequence of period, known as \textit{terms}, and the first term is known as the \textit{bootstrap term}. Each term, with the exception of the bootstrap term, has a corresponding \textit{council}, which is a set of staked members responsible for voting over submitted \textit{proposals}. Proposals are bids to execute given operations on the platform state in order to serve some contemplated end.

>>>>

      \item[-] \textbf{Added:} Date and time when the membership was first established .
      \item[-] \textbf{Entry:} If membership was established through screening (see section \ref{sec:membership_curation}), the this is set to ID of screening authority which created membership. If it was established through payment (see section \ref{sec:paid_membership}), then this is the paid term ID of the terms. Otherwise its blank.
      \item[-] \textbf{BRAQs Instances:} Set of BRAQ instances for all base member actions (see section \ref{sec:BRAQ})
      \item[-] \textbf{Suspended:} Whether member is suspended.
      \item[-] \textbf{Subscription:} If at least one subscription has been entered into, then this is the date and time of this, and the corresponding subscription term ID (see section \ref{sec:subscription}). Otherwise its blank.
    \end{itemize}
\end{concept_box}

@@

The governance process is divided into a sequence of periods, known as \textit{terms}, and the first term is known as the \textit{bootstrap term}. Each term, with the exception of the bootstrap term, has a corresponding \textit{council}, which is a set of staked members responsible for voting over submitted \textit{proposals}. Proposals are bids to execute given operations on the platform state in order to serve some contemplated end.
